Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-22 WSSSPE3/report/WSSSPE3_review.tex
Section 3: Keynote: Definitions of sustainability.

>>>>

Turk then moved onto various different definitions of sustainability. His most
favourite one was keeping up with bug reports, in which case even if no new
features were added, the software remains sustainable. Another definition of
sustainability Turk mentioned was adding on new features, or maintaining the
software for a long period of time such as the cases of TeX or LaTeX with
community help. A notion Turk heard often at supercomputing conferences was that
sustainable software continued to work on new architectures. Yet another metric
was people continuing to be able to learn how to use and apply the software.
Some funder Turk heard talked about sustainability as getting funded. Turk also
recalled that Greg Wilson said in WSSSPE 1.1 in his view sustainable software
was software that continued to give the same results over time. A last measure
of sustainability Turk presented was the ability to transition between different people
developing and using a piece of software.
